Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete

### 2019-05-24 analysis/paper/JMAArticle.Rmd
Further edits and new Figures

## The Early Iron Age Cemeteries
```{r map, fig.cap="Map of the Knossos area showing the locations of the various tomb clusters and cemeteries, with EIA pottery distributions from the KULP marked in orange"}
knitr::include_graphics("../figures/Knossos Tombs Map.png")
```

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

The 12 tombs with the most associated vessels are all chamber tombs, with 10 dating to the 9th century, and two to the 10th. And, in Figure \@ref(fig:toptombs), we see that seven of the 12 did exhibit late, intense episodes of deposition. Tombs P, 292, 75, 107, 285, II, 218, and 104 between them accrount for `r round(calc1,digits=2)`% of the entire pottery assemblage recovered from the `r nrow(tombs)` tombs considered here. All but Tomb 285 date to the 9th century, and together they underpinned the late spate of burials here considered. Interestingly, Tombs X, G, Q, 104 and 283, however, evince a different pattern, with their respective peaks coming in the PGB and EG periods, around a century earlier. We have seen already in Figure \@ref(fig:aoristbycem) that, particularly in the KNC, the end of the 9th century was another period of increased burial activity. What, then, set these two groups of tombs apart? The recipients of the greatest numbers of burials and grave goods in both cemeteries, they nonetheless seem to have achieved that distinction via different histories. By looking more closely at the periods in which they were built, and in which they were most popular, I hope to shed light on the broader social contexts in which these tombs were flourished.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

## The Early Iron Age Cemeteries

@@

Insert Figure \@ref(fig:burialestimate) around here

@@

Insert Figure \@ref(fig:allpithoi) about here

@@

Insert Figure \@ref(fig:aoristallcems) around here

@@

Insert Figure \@ref(fig:aoristbycem) around here

@@

Insert Figure \@ref(fig:tombconstruction) around here

@@

Insert Figure \@ref(fig:tombsinuse) around here

@@

Insert Figure \@ref(fig:tombsinusebybuilddate) around here

@@

Insert Figure \@ref(fig:potsbydateandtombdate) around here

@@

Insert Table 1 around here

@@

Insert Figure \@ref(fig:toptombs) around here

```{r calc}

@@

```
The 12 tombs with the most associated vessels are all chamber tombs, with 10 dating to the 9th century, and two to the 10th. And, in Figure \@ref(fig:toptombs), we see that seven of the 12 did exhibit late, intense episodes of deposition. Tombs P, 292, 75, 107, 285, II, 218, and 104 between them accrount for `r round(calc1,digits=2)`% of the entire pottery assemblage recovered from the `r nrow(tombs)` tombs considered here. All but Tomb 285 date to the 9th century, and together they underpinned the late spate of burials here considered. Interestingly, Tombs X, G, Q, 104 and 283, however, evince a different pattern, with their respective peaks coming in the PGB and EG periods, around a century earlier. We have seen already in Figure \@ref(fig:aoristbycem) that, particularly in the KNC, the end of the 9th century was another period of increased burial activity. What, then, set these two groups of tombs apart? The recipients of the greatest numbers of burials and grave goods in both cemeteries, they nonetheless seem to have achieved that distinction via different histories. By looking more closely at the periods in which they were built, and in which they were most popular, I hope to shed light on the broader social contexts in which these tombs were flourished.

@@

Insert Figure \@ref(fig:tombdimensions) around here

@@

Insert Figure \@ref(fig:dimensionsboxplots) around here

@@

Insert Figure \@ref(fig:tombscompthroughtime) around here

@@

Insert Figure \@ref(fig:imports) around here

@@

Insert Figure \@ref(fig:importstombcenturies) around here

@@

Inset Figure \@ref(fig:bigbox)

@@

Insert Figure \@ref(fig:gini) around here

@@

Insert Figure \@ref(fig:comps) around here

@@

Insert Figure \@ref(fig:hists) around here

@@

# Captions

# Figures

```{r map, fig.cap="Map of the Knossos area showing the locations of the various tomb clusters and cemeteries, with EIA pottery distributions from the KULP marked in orange"}
knitr::include_graphics("../figures/Knossos Tombs Map.png")
```

# Tables
